No Massive Companion to the Low-Frequency, Coherent Radio-Emitting M~Dwarf GJ\,1151

### 2019-08-29 paper/ms.tex
pdf figures
apw as author
lower mass estimate

@@

Using these data we do not detect a clear planetary signal, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ\,1151 at 5.1~\mearth.

@@

\begin{figure}
\plotone{gj1151b_samples_trend.png}
\caption{\label{jokermodel1151}
\textit{The Joker} posterior samples for GJ\,1151.
}
\end{figure}

\begin{figure}
\plotone{cornerplot_km_trend.png}

>>>>

\author[0000-0003-0872-7098]{Adrian Price-Whelan}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

@@

Using these data we do not detect a clear planetary signal, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ\,1151 at 3.5~\mearth.

@@

\begin{figure}
\plotone{gj1151b_samples_trend.pdf}
\caption{\label{jokermodel1151}
\textit{The Joker} posterior samples for GJ\,1151.
}
\end{figure}

\begin{figure}
\plotone{cornerplot_km_trend.pdf}
